### 2019-04-08 papers/journal/synth-dia.tex
Intro Dia fixed

%\begin{tikzpicture}[->,>=stealth',shorten >=1pt,auto,node distance=2cm,
%thick,main node/.style={circle,draw,font=\sffamily,minimum size=0.8cm}]
%\begin{scope}[]
%
%\node[main node] (1) {$s_{1}$};
%\node[main node] (2) [below left of=1] {$s_{2}$};
%\node[main node] (3) [below right of=1] {$s_{3}$};
%
%\path[every node/.style={font=\sffamily\small}]
%(3) edge node [left] {} (1)
%(1) edge [loop above] node {} ()
%(2) edge [loop above] node {} ()
%(1) edge node [right] {} (2)
%(2) edge node[right] {} (3)
%(3) edge[bend left, below] node{} (2);
%%(3) edge [bend right] node[right] {} (2)
%\end{scope}
 \begin{tikzpicture}[->,>=stealth', auto , node distance=3.1cm,
	  thick,main node/.style={rectangle,draw,rounded corners}]
	 % 	\begin{scope}[]
	  \node[main node, text width=1.5cm] (pm) {\textbf{PM:} { {$Q_{a5}$} 
	  		                     {$Q_{a7}$} {$Q_{bc2}$} {$Q_{bc7}$}}};
	  \node[main node, text width=1.5cm] (ee) [below right of=pm] {\textbf{EE:} { {$Q_{a2}$} {$ Q_{b2/3} $} {$ Q_{c2/3} $}}};
	  \node[main node, text width=1.3cm] (le) [above of=ee,yshift=-10mm,xshift=20mm] {\textbf{LE:} { {$Q_{a8}$} {$Q_{b8}$} {$Q_{c8}$}}};

	  %le <-> pm
	  \path (le) edge[bend right=55] node [above] {$Q_{b7}$, $Q_{c7}$} (pm);
	  \path (ee) edge[bend right=32, text width=1.8cm] node [below,right=0.1] {{$R_{8}$}, $Q_{a7}$, $Q_{b7}$, $R_{7}$} (le);

	  %pm <-> ee
	  \path (ee) edge[bend left=32] node [below] {{$R_{3}$}} (pm);
	  \path (pm) edge[bend left=30, text width=2.0cm] node [above,rotate=-45] {{$R_{2}$}, {$Q_{a7}$} $Q_{bc7}$, $R_{7}$, $Q_{c7}$, $Q_{a2}$} (ee);
	\end{tikzpicture}
	\caption{Input partial VTS} 
		 \label{fig:synth-vts1}
  \end{subfigure}%
 % \end{scope}
%  \vspace{1.2cm}
  \begin{subfigure}[b]{0.49\linewidth}
	  \begin{tikzpicture}[->,>=stealth',auto,node distance=3.5cm,
	  thick,main node/.style={rectangle,draw,rounded corners}]
	 % \begin{scope}[xshift=3.5cm,yshift=0.0cm]
	  \node[main node, text width=1.5cm] (pm) {\textbf{PM:} { {$Q_{a5}$} 
	  	  		                     {$Q_{a7}$} {$Q_{bc2}$} {$Q_{bc7}$} ...}};
	  	  \node[main node, text width=1.5cm] (ee) [below right of=pm] {\textbf{EE:} { {$Q_{a2}$} {$ Q_{b2/3} $} {$ Q_{c2/3} $} ...}};
	  	  \node[main node, text width=1.3cm] (le) [above of=ee,yshift=-10mm,xshift=20mm] {\textbf{LE:} { {$Q_{a8}$} {$Q_{b8}$} {$Q_{c8}$} ...}};

	  %le <-> pm
	  	  \path (le) edge[bend right=45] node [above] {$Q_{b7}$, $Q_{c7}$,{\color{blue}{ \textbf{$R_{7}$}}}} (pm);
	%  \path (le) edge[bend right=45] node [above] {Qb7 Qc7,{\color{blue} { \textbf{R7}}}} (pm);

	  %le <-> ee
	  {\color{red} { \path (le) edge[bend right] node [below,rotate=50] {{\color{blue} { {\textbf{{$R_{8}$}}}}}{\color{black},} {\color{blue} {$Q_{a7}$}}} (ee);
	  }}
	  %ee -> le
	   \path (ee) edge[bend right=32, text width=1.8cm] node [below,right=0.1] {{$R_{8}$}, $Q_{a7}$, $Q_{b7}$, $R_{7}$} (le);
%	  \path (ee) edge[bend right] node [text width=1.5cm, below,rotate=50] {{R8}, Qa7, Qbc7,R7} (le);

	  %pm <-> ee
	  \path (ee) edge[bend left=30] node [below, text width=2.0cm] {{$R_{3}$,{\color{blue} { \textbf{{$Q_{a2} $}}}}, {\color{blue} {{ $ Q_{a7}$}}}, {\color{blue} {{$R_{2}$}}}}} (pm);
	   \path (pm) edge[bend left=30, text width=2.3cm] node [above,rotate=-45] {{$R_{2}$}, {$Q_{a7}$} $Q_{bc7}$, $R_{7}$, $Q_{c7}$, $Q_{a2}$} node [below,anchor=center] {\color{blue} { \textbf{$R_{3}$}}} (ee);
%	  \path (pm) edge[bend left=30] node [above,rotate=-45,text width = 2.5cm] {{R2} {Qa7} Qbc7, R7, Qc7, Qa2, \color{blue} { \textbf{R3}}} (ee);	    
	 % \end{scope}

>>>>

%\begin{tikzpicture}[->,>=stealth',shorten >=1pt,auto,node distance=2cm,
%thick,main node/.style={circle,draw,font=\sffamily,minimum size=0.8cm}]
%\begin{scope}[]
%
%\node[main node] (1) {$s_{1}$};
%\node[main node] (2) [below left of=1] {$s_{2}$};
%\node[main node] (3) [below right of=1] {$s_{3}$};
%
%\path[every node/.style={font=\sffamily\small}]
%(3) edge node [left] {} (1)
%(1) edge [loop above] node {} ()
%(2) edge [loop above] node {} ()
%(1) edge node [right] {} (2)
%(2) edge node[right] {} (3)
%(3) edge[bend left, below] node{} (2);
%%(3) edge [bend right] node[right] {} (2)
%\end{scope}
 \begin{tikzpicture}[->,>=stealth', auto , node distance=3.1cm,
	  thick,main node/.style={rectangle,draw,rounded corners}]
	 % 	\begin{scope}[]
	  \node[main node, text width=1.5cm] (pm) {$\mathbf{N_{0}}$: { {$Q_{a5}$} 
	  		                     {$Q_{a7}$} {$Q_{bc2}$} {$Q_{bc7}$}}};
	  \node[main node, text width=1.5cm] (ee) [below right of=pm] {$\mathbf{N_{1}}$: { {$Q_{a2}$} {$ Q_{b2/3} $} {$ Q_{c2/3} $}}};
	  \node[main node, text width=1.3cm] (le) [above of=ee,yshift=-10mm,xshift=20mm] {$\mathbf{N_{2}}$: { {$Q_{a8}$} {$Q_{b8}$} {$Q_{c8}$}}};

	  %le <-> pm
	  \path (le) edge[bend right=55] node [above] {$Q_{bc7}$} (pm);
	  \path (ee) edge[bend right=32, text width=1.8cm] node [below,right=0.1] {{$R_{8}$}, $Q_{a7}$, $Q_{bc7}$, $R_{7}$} (le);

	  %pm <-> ee
	  \path (ee) edge[bend left=32] node [below] {{$R_{3}$}} (pm);
	  \path (pm) edge[bend left=30, text width=2.1cm] node [above,rotate=-45] {{$R_{2}$}, {$Q_{a7}$}, $Q_{bc7}$, $R_{7}$, $Q_{a2}$} (ee);
	\end{tikzpicture}
	\caption{Input partial VTS} 
		 \label{fig:synth-vts1}
  \end{subfigure}%
 % \end{scope}
%  \vspace{1.2cm}
  \begin{subfigure}[b]{0.49\linewidth}
	  \begin{tikzpicture}[->,>=stealth',auto,node distance=3.5cm,
	  thick,main node/.style={rectangle,draw,rounded corners}]
	 % \begin{scope}[xshift=3.5cm,yshift=0.0cm]
	  \node[main node, text width=1.5cm] (pm) {$\mathbf{N_{0}}$: { {$Q_{a5}$} 
	  	  		                     {$Q_{a7}$} {$Q_{bc2}$} {$Q_{bc7}$}}...};
	  	  \node[main node, text width=1.5cm] (ee) [below right of=pm] {$\mathbf{N_{1}}$: { {$Q_{a2}$} {$ Q_{b2/3} $} {$ Q_{c2/3} $}}...};
	  	  \node[main node, text width=1.3cm] (le) [above of=ee,yshift=-10mm,xshift=20mm] {$\mathbf{N_{2}}$: { {$Q_{a8}$} {$Q_{b8}$} {$Q_{c8}$}}...};

	  %le <-> pm
	  	  \path (le) edge[bend right=45] node [above] {$Q_{bc7}$,{\color{blue}{ \textbf{$R_{7}$}}}} (pm);
	%  \path (le) edge[bend right=45] node [above] {Qb7 Qc7,{\color{blue} { \textbf{R7}}}} (pm);

	  %le <-> ee
	  {\color{red} { \path (le) edge[bend right] node [below,rotate=50] {{\color{blue} { {\textbf{{$R_{8}$}}}}}{\color{black},} {\color{blue} {$Q_{a7}$}}} (ee);
	  }}
	  %ee -> le
	   \path (ee) edge[bend right=32, text width=1.8cm] node [below,right=0.1] {{$R_{8}$}, $Q_{a7}$, $Q_{bc7}$, $R_{7}$} (le);
%	  \path (ee) edge[bend right] node [text width=1.5cm, below,rotate=50] {{R8}, Qa7, Qbc7,R7} (le);

	  %pm <-> ee
	  \path (ee) edge[bend left=30] node [below, text width=2.0cm] {{$R_{3}$,{\color{blue} { \textbf{{$Q_{a2} $}}}}, {\color{blue} {{ $ Q_{a7}$}}}, {\color{blue} {{$R_{2}$}}}}} (pm);
	   \path (pm) edge[bend left=30, text width=2.3cm] node [above,rotate=-45] {{$R_{2}$}, {$Q_{a7}$}, $Q_{bc7}$ $R_{7}$, $Q_{a2}$, \color{blue} {$R_{3}$}} (ee);
%	  \path (pm) edge[bend left=30] node [above,rotate=-45,text width = 2.5cm] {{R2} {Qa7} Qbc7, R7, Qc7, Qa2, \color{blue} { \textbf{R3}}} (ee);	    
	 % \end{scope}
